|

### 2020-03-11 paper/Manuscript.Rmd
Add Jeroen Ooms to acknowledgements
remove motley

authornote: |
  This is a preprint, not a peer-reviewed publication. Comments, contributions,
  and coauthors are welcome. Please contact the lead author.
keywords          : "open science; reproducibility; r; dynamic document generation; version control"
wordcount         : "5921"

@@

```{r load_packages, include = FALSE}
library("papaja")
library(motley)
mask <- TRUE
masked <- function(text){
  ifelse(mask, "[masked]", text)
}
```

>>>>

authornote: |
  This is a preprint, not a peer-reviewed publication. Comments, contributions,
  and coauthors are welcome. Please contact the lead author.
  Acknowledgements: Jeroen Ooms (feedback, suggesting gert, and using Remotes
  field).
keywords          : "open science; reproducibility; r; dynamic document generation; version control"
wordcount         : "5921"

@@

```{r load_packages, include = FALSE}
library("papaja")
mask <- TRUE
masked <- function(text){
  ifelse(mask, "[masked]", text)
}
```
